Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-06 manuscript/manuscript.Rmd
typo
bit more rl

In our case, the environment will be a computational model of the population dynamics of a fishery, with the environment state being a vector of all the fish populations, $S=(V_1, V_2, H)$.
The system evolves naturally according to \eqref{eq:3d model}.
At each time step, the agent harvests one of the populations, say $A$. 
Specifically, it chooses a quota $q$: the fraction of $A$ that will be fished.
This changes the state as
\begin{align*}
  (V_1,\ V_2,\ H) \mapsto ((1-q)V_1,\ V_2,\ H)
\end{align*}
and secures a reward of $qA$ to the agent.
Afterwards, the environment undergoes its natural dynamics.

>>>>

In our case, the environment will be a computational model of the population dynamics of a fishery, with the environment state being a vector of all the fish populations, $S=(V_1, V_2, H)$.
The system evolves naturally according to \eqref{eq:3d model}.
At each time step, the agent harvests one of the populations, say $A$. 
Specifically, it chooses a quota $q$: the fraction of $A$ that will be fished.
This changes the state as
\begin{align*}
  (V_1,\ V_2,\ H) \mapsto ((1-q)V_1,\ V_2,\ H)
\end{align*}
and secures a reward of $qV_1$ to the agent.
Afterwards, the environment undergoes its natural dynamics.

## Mathematical framework for RL

Mathematically, RL may be formulated using a discrete time *partially observable Markov decision process (POMDP)*.
This formalization is rather flexible and allows one, e.g., to account for situations where the agent may not fully observe the environment state, or where the only observations available to the agent are certain functions of the underlying state.
For the sake of clarity, we will present here only the class of POMDPs which are relevant to our work: fully observed POMDPs with trivial emission function (FMDPs for short).
An FMDP may be defined by the following data:
- $\mathcal{S}$: *state space*, the set of states of the environment,
- $\mathcal{A}$: *action space*, the set of actions which the agent may choose from,
- $T(s_{t+1}|s_t, a_t)$: *transition operator*, a conditional distribution which describes the dynamics of the system,
- $r(s_t, a_t)$: *reward function*, the reward obtained after performing action $a_t\in\mathcal{A}$ in state $s_t$,
- $d(s_0)$: *initial state distribution*, the initial state of the environment is sampled from this distribution,
- $\gamma\in[0,1]$: *discount factor*.
